\documentclass[12pt]{article}

\usepackage{graphicx}
\usepackage{paralist}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{hhline}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{url}

\oddsidemargin -10mm
\evensidemargin -10mm
\textwidth 160mm
\textheight 200mm
\renewcommand\baselinestretch{1.0}

\pagestyle {plain}
\pagenumbering{arabic}

\newcounter{stepnum}

%% Comments

\usepackage{color}

\newif\ifcomments\commentstrue

\ifcomments
\newcommand{\authornote}[3]{\textcolor{#1}{[#3 ---#2]}}
\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
\else
\newcommand{\authornote}[3]{}
\newcommand{\todo}[1]{}
\fi

\newcommand{\wss}[1]{\authornote{blue}{SS}{#1}}

\title{Assignment 3, Part 1, Specification}
\author{SFWR ENG 2AA4}

\begin {document}

\maketitle
This Module Interface Specification (MIS) document contains modules, types and
methods for implementing a generic 2D sequence that is instantiated for both
land use planning and for a Discrete Elevation Model (DEM).

In applying the specification, there may be cases that involve undefinedness.
We will interpret undefinedness following~\cite{Farmer2004}:

If $p: \alpha_1 \times .... \times \alpha_n \rightarrow \mathbb{B}$ and any of
$a_1, ..., a_n$ is undefined, then $p(a_1, ..., a_n)$ is False.  For instance,
if $p(x) = 1/x < 1$, then $p(0) = \text{False}$.  In the language of our
specification, if evaluating an expression generates an exception, then the
value of the expression is undefined.

\wss{The parts that you need to fill in are marked by comments, like this one.
  In several of the modules local functions are specified.  You can use these
  local functions to complete the missing specifications.}

\wss{As you edit the tex source, please leave the \texttt{wss} comments in the
  file.  Put your answer \textbf{after} the comment.  This will make grading
  easier.}

\bibliographystyle{plain}
\bibliography{SmithCollectedRefs}

\newpage

\section* {Land Use Type Module}

\subsection*{Module}

LanduseT

\subsection* {Uses}

N/A

\subsection* {Syntax}

\subsubsection* {Exported Constants}

None

\subsubsection* {Exported Types}

Landtypes = \{R, T, A, C\}\\

\noindent \textit{//R stands for Recreational, T for Transport, A for Agricultural, C for
  Commercial}

\subsubsection* {Exported Access Programs}

\begin{tabular}{| l | l | l | p{5cm} |}
\hline
\textbf{Routine name} & \textbf{In} & \textbf{Out} & \textbf{Exceptions}\\
\hline
new LanduseT & Landtypes & LanduseT & ~\\
\hline
\end{tabular}

\subsection* {Semantics}

\subsubsection* {State Variables}

landuse: Landtypes

\subsubsection* {State Invariant}

None

\subsubsection* {Access Routine Semantics}

\noindent new LandUseT($t$):
\begin{itemize}
\item transition: $\mathit{landuse} := t$
\item output: $out := \mbox{self}$
\item exception: none
\end{itemize}

\subsubsection* {Considerations}

When implementing in Java, use enums (as shown in Tutorial 06 for ElementT).

\newpage

\section* {Point ADT Module}

\subsection*{Template Module inherits Equality(PointT)}

PointT

\subsection* {Uses}

N/A

\subsection* {Syntax}

\subsubsection* {Exported Types}


\wss{What should be written here?}  PointT = ?

\subsubsection* {Exported Access Programs}

\begin{tabular}{| l | l | l | l |}
\hline
\textbf{Routine name} & \textbf{In} & \textbf{Out} & \textbf{Exceptions}\\
\hline
PointT & $\mathbb{Z}$, $\mathbb{Z}$ & PointT & \\
\hline
row & ~ & $\mathbb{Z}$ & ~\\
\hline
col & ~ & $\mathbb{Z}$ & ~\\
\hline
translate & $\mathbb{Z}$, $\mathbb{Z}$ & PointT & ~\\
\hline
\end{tabular}

\subsection* {Semantics}

\subsubsection* {State Variables}

$r:$ \wss{What is the type of the state variables?} $\mathbb{Z}$  \\ 
$c:$ \wss{What is the type of the state variables?} $\mathbb{Z}$

\subsubsection* {State Invariant}

None

\subsubsection* {Assumptions}

The constructor PointT is called for each object instance before any other
access routine is called for that object.  The constructor cannot be called on
an existing object.

\subsubsection* {Access Routine Semantics}

PointT($row, col$):
\begin{itemize}
\item transition: \wss{What should the state transition be for the constructor?} $r, c := row, col$ 
\item output: $out := \mathit{self}$
\item exception: None
\end{itemize}

\noindent row():
\begin{itemize}
\item output: $out := r$
\item exception: None
\end{itemize}

\noindent col():
\begin{itemize}
\item output: \wss{What should go here?} $out := c$
\item exception: None
\end{itemize}

\noindent translate($\Delta r$, $\Delta c$):
\begin{itemize}
\item output: \wss{What should go here?}  $out :=\mbox{PointT}(r + \Delta r, c + \Delta c)$
\item exception: \wss{What should go here?}  None
\end{itemize}

\newpage

\section* {Generic Seq2D Module}

\subsection* {Generic Template Module}

Seq2D(T)

\subsection* {Uses}

PointT

\subsection* {Syntax}

\subsubsection* {Exported Types}

Seq2D(T) = ?

\subsubsection* {Exported Constants}

None

\subsubsection* {Exported Access Programs}

\begin{tabular}{| l | l | l | p{6cm} |}
\hline
\textbf{Routine name} & \textbf{In} & \textbf{Out} & \textbf{Exceptions}\\
\hline
Seq2D & seq of (seq of T), $\mathbb{R}$ & Seq2D & IllegalArgumentException\\
\hline
set & PointT, T & ~ & IndexOutOfBoundsException\\
\hline
get & PointT & T & IndexOutOfBoundsException\\
\hline
getNumRow & ~ & $\mathbb{N}$ & \\
\hline
getNumCol & ~ & $\mathbb{N}$ & \\
\hline
getScale & ~ & $\mathbb{R}$ & \\
\hline
count & T & $\mathbb{N}$ & \\
\hline
countRow & T, $\mathbb{N}$ & $\mathbb{N}$ & IndexOutOfBoundsException\\
\hline
area & T & $\mathbb{R}$ & \\
\hline
\end{tabular}

\subsection* {Semantics}

\subsubsection* {State Variables}

$s$: seq of (seq of T)\\
scale: $\mathbb{R}$\\
nRow: $\mathbb{N}$\\
nCol: $\mathbb{N}$

\subsubsection* {State Invariant}

None

\subsubsection* {Assumptions}

\begin{itemize}
\item The Seq2D(T) constructor is called for each object instance before any
other access routine is called for that object.  The constructor can only be
called once.
\item Assume that the input to the constructor is a sequence of rows, where each
  row is a sequence of elements of type T.  The number of columns (number of
  elements) in each row is assumed to be equal. That is each row
  of the grid has the same number of entries.  $s[i][j]$ means the ith row and
  the jth column.  The 0th row is at the top of the grid and the 0th column
  is at the leftmost side of the grid.
\end{itemize}

\subsubsection* {Access Routine Semantics}

Seq2D($S$, scl):
\begin{itemize}	
\item transition: \wss{Fill in the transition.}  $s, scale, nRow, nCol:= S, scl,  |S[0]|, |S| $
\item output: $\mathit{out} := \mathit{self}$
\item exception: \wss{Fill in the exception.  One should be generated if the
    scale is less than zero, or the input sequence is empty, or the number of
    columns is zero in the first row, or the number of columns in any row is
    different from the number of columns in the first row.}\\
$(scale \le 0 \lor |S| = 0 \lor |S[0]| = 0 \lor \lnot\forall(l : \mbox{seq of T}|l\in S: |l| = |S[0]|)) \implies \mbox{IllegalArgumentException}$  
\end{itemize}

\noindent set($p, v$):
\begin{itemize}
\item transition: \wss{?} $s[p.r][p.c] := v$
\item exception: \wss{Generate an exception if the point lies outside of the
    map.}\\ 
$\lnot validPoint(p) \implies \mbox{IndexOutOfBoundsException}$
\end{itemize}

\noindent get($p$):
\begin{itemize}
\item output: \wss{?} $out := s[p.r][p.c]$
\item exception: \wss{Generate an exception if the point lies outside of the map.}
$\lnot validPoint(p) \implies \mbox{IndexOutOfBoundsException}$
\end{itemize}

\noindent getNumRow():
\begin{itemize}
\item output: $out := \mbox{nRow}$
\item exception: None
\end{itemize}

\noindent getNumCol():
\begin{itemize}
\item output: $out := \mbox{nCol}$
\item exception: None
\end{itemize}

\noindent getScale():
\begin{itemize}
\item output: $out := \mbox{scale}$
\item exception: None
\end{itemize}

\noindent count($t$: T):
\begin{itemize}
\item output: \wss{Count the number of times the value $t$ occurs in the 2D sequence.}\\
$out := +(i,j : \mathbb{N} | \mbox{validRow}(i) \land \mbox{validCol}(j) \land s[i][j] = t : 1) $
\item exception: None
\end{itemize}

\noindent countRow($t$: T, $i: \mathbb{N}$):
\begin{itemize}
\item output: \wss{Count the number of times the value $t$ occurs in row $i$.}\\
$out := +(j : \mathbb{N} | \mbox{validRow}(i) \land \mbox{validRow}(j) \land s[i][j] = t : 1)  $ 
\item exception: \wss{Generate an exception if the index is not a valid row.}\\
$\lnot \mbox{validRow}(i) \implies \mbox{IndexOutOfBoundsException}$
\end{itemize}

\noindent area($t$: T):
\begin{itemize}
\item output: \wss{Return the total area in the grid taken up by cell value $t$.
    The length of each side of each cell in the grid is
    scale.}\\
$out := count(t) * scale$
\item exception: None
\end{itemize}

\subsection*{Local Functions}

\noindent validRow: $\mathbb{N} \rightarrow \mathbb{B}$\\
\noindent \wss{returns true if the given natural number is a valid row number.}\\ 
$\mbox{validRow}(i) \equiv 0 \le i \le (\mbox{nRow} - 1)$ \\

\noindent validCol: $\mathbb{N} \rightarrow \mathbb{B}$\\
\noindent \wss{returns true if the given natural number is a valid column
  number.}\\
$\mbox{validCol}(j) \equiv 0 \le j \le (\mbox{nCol} - 1)$ \\

\noindent validPoint: $\mbox{PointT} \rightarrow \mathbb{B}$\\
\noindent \wss{Returns true if the given point lies within the boundaries of the
  map.}\\
$\mbox{validPoint}(p) \equiv \mbox{validRow}(p.r) \land \mbox{validCol}(p.c)$

\newpage

\section* {LanduseMap Module}

\subsection* {Template Module}

\wss{Instantiate the generic ADT Seq2D(T) with the type LanduseT}\\
LanduseMapT is Seq2D(LanduseT)

\newpage

\section* {DEM Module}

\subsection* {Template Module}

DemT is Seq2D($\mathbb{Z}$)

\subsection* {Syntax}

\subsubsection* {Exported Access Programs}

\begin{tabular}{| l | l | l | p{6cm} |}
\hline
\textbf{Routine name} & \textbf{In} & \textbf{Out} & \textbf{Exceptions}\\
\hline
total & & $\mathbb{Z}$ & \\
\hline
max &  & $\mathbb{Z}$ & \\
\hline
ascendingRows & & $\mathbb{B}$ & \\
\hline
\end{tabular}

\subsection* {Semantics}

\subsubsection* {Access Routine Semantics}

\noindent total():
\begin{itemize}
\item output: \wss{Total of all the values in all of the cells.}\\
$out := +(i,j : \mathbb{N}| \mbox{validRow}(i) \land  \mbox{validCol}(j) : s[i][j])$
\item exception: None
\end{itemize}

\noindent max():
\begin{itemize}
\item output: \wss{Find the maximum value in the 2d grid of integers}
\item exception: None
\end{itemize}

\noindent ascendingRows():
\begin{itemize}
\item output: \wss{Returns True if the sum of all values in each row increases
    as the row number increases, otherwise, returns False.}\\
$out := \forall i, j: $
\item exception: None
\end{itemize}

\subsection*{Local Functions}

\noindent validRow: $\mathbb{N} \rightarrow \mathbb{B}$\\
\noindent \wss{returns true if the given natural number is a valid row number.}\\ 
$\mbox{validRow}(i) \equiv 0 \le i \le (\mbox{nRow} - 1)$ \\

\noindent validCol: $\mathbb{N} \rightarrow \mathbb{B}$\\
\noindent \wss{returns true if the given natural number is a valid column
  number.}\\
$\mbox{validCol}(j) \equiv 0 \le j \le (\mbox{nCol} - 1)$ \\

\newpage

\section*{Critique of Design}

\wss{Write a critique of the interface for the modules in this project.  Is there
anything missing?  Is there anything you would consider changing?  Why?  One
thing you could discuss is that the Java implementation, following the notes
given in the assignment description, will expose the use of ArrayList for Seq2D.
 How might you change this?  There are repeated local functions in two modules.
What could you do about this?}\\\\
One such change that I would consider changing is to have the DEM module to also inherit the local functions (eg. validRow).
Since these functions provide the same purpose in both modules, we do not need to instantiate these functions in both the Seq2D and DEM module. 
This would improve the modularity and simplicity of the specification. 
In addition, declaring in the specification to utilize ArrayLists defeats the idea of abstraction, as it reveals the implementation details to the 
user/client. Rather, the specification should allow the programmer to utilize whatever type that they feel is most suitable. \\\\


In addition to your critique, please address the following questions:

\begin{enumerate}
\item The original version of the assignment had an Equality interface defined
  as for A2, but this idea was dropped.  In the original version Seq2D inherited
  the Equality interface.  Although this works in Java with the LanduseMapT, it is
  problematic for DemT.  Why is it problematic?  (Hint: DEMT is instantiated
  with the Java type Integer.)
\item Although Java has several interfaces as part of the standard language,
  such as the Comparable interface, there is no Equality interface.  Instead
  equals is provided through inheritance from Object.  Why do you think the
  Java language designers decided to use inheritance for equality, instead of
  providing an interface?
\item The qualities of good module interface push the design of the interface in
  different directions. Why is it rarely possible to achieve a module interface
  that simultaneously is essential, minimal and general?
\end{enumerate}

\begin{enumerate}
\item 

\item 
Java utilizes inheritance for equality, rather than an interface, because it's simple to implement an equals() method that works for both primitive and built-in object types (like String and Arraylist).
Since types like String and Arraylist act as objects in java and are commonly used in programs all the time, it makes sense that Java designers ensured that equals() works with object types. If a developer 
wished to use equals(), all they have to do is to create an override equals() method that handles equality for a custom object type.

\item 



\end{enumerate}


\end {document}